---
output: github_document
bibliography: vignettes/references.bib
link-citations: TRUE
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# kernopt - A R Package for estimating count data distributions with a Discrete Symmetric Optimal Kernel

<!-- badges: start -->
 [![CRAN status](https://www.r-pkg.org/badges/version/kernopt)](https://cran.r-project.org/package=kernopt)
 [![R-CMD-check](https://github.com/thomasfillon/kernopt/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/thomasfillon/kernopt/actions/workflows/R-CMD-check.yaml)
 [![Codecov test coverage](https://codecov.io/gh/thomasfillon/kernopt/graph/badge.svg)](https://app.codecov.io/gh/thomasfillon/kernopt)
<!-- badges: end -->

## kernopt: 
**kernopt** is an R package that implements *Discrete Symmetric Optimal Kernel* for estimating count data distributions, as described by [@SengaDurrieu2024].
The non parametric estimator using the discrete symmetric optimal kernel was illustrated on simulated data sets and a real-word data set included in the package, in comparison with two other discrete symmetric kernels the *triangular kernel* and the *Epanechnikov kernel* and with the discrete binomial kernel.

## Authors: 
- *Tristan Senga Kiessé*, UMR SAS INRAE, Institut Agro
- *Gilles Durrieu*, Université Bretagne Sud - CNRS UMR 6205, LMBA
- *Thomas Fillon*, Université Bretagne Sud - CNRS UMR 6205, LMBA & CNRS UMR 6074 IRISA


## Installation

You can install the development version of kernopt from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("thomasfillon/kernopt")
```

## Example

This is a basic example which shows how to use the *kernopt* library to compute the discrete optimal kernel values for some parameters:

```{r example}
library(kernopt)

## Compute the discrete optimal kernel values
k_opt <- discrete_optimal(x = 25, z = 1:50, h = 0.9, k = 20)
print(k_opt)
```

The documentation is available at <https://thomasfillon.github.io/kernopt>.



## References
